% !TEX root = ../main.tex

\pagenumbering{roman}

     \vspace*{2ex}
     \begin{center}
       {\bf Rethinking Certificate Authorities: \\Understanding and decentralizing domain validation}\\
       {\bf  }
     \end{center}
     \vspace{10ex}
     \begin{center}
	Seyedehmahsa Moosavi
     \end{center}
     \vspace{11ex}
     \begin{center}
        A thesis in the
     \end{center}
     \begin{center}
        Concordia Institute for Information Systems Engineering
     \end{center}
     \vspace{14ex}
     \begin{center}
        Presented in Partial Fulfilment of the Requirements for
     \end{center}
     \vspace*{-3ex}
     \begin{center}
        the Degree of Master of Applied Science at
     \end{center}
     \vspace*{-3ex}
     \begin{center}
        Concordia University
     \end{center}
     \vspace*{-3ex}
     \begin{center}
        Montr\'{e}al, Qu\'{e}bec, Canada
     \end{center}
     \vspace{10ex}
     \begin{center}
        \today
     \end{center}
 
 \clearpage
 
     \vspace*{1ex}
     \begin{center}
        CONCORDIA UNIVERSITY
     \end{center}
     \begin{center}
        Division of Graduate Studies
     \end{center}
     \vspace{3ex}
     This is to certify that the thesis prepared\\[2ex]
     By :\hspace{40pt}{\bf Seyedehmahsa Moosavi}\\[2ex]
     Entitled :\hspace*{13pt}{\bf Rethinking Certificate Authorities: \\Understanding and decentralizing domain validation}\\ 
     \hspace*{62pt}{\bf } \\[2ex]
    and submitted in partial fulfilment of the requirements for the degree
    of\\[2ex]
    \hspace*{62pt}{\bf Master of Applied Science}\\[2ex]
    complies with the regulations of this University and meets the accepted
    standards with respect to originality and quality. \\[2ex]
    Signed by the final examining committee : \\[5ex]
    \hspace*{77pt}\underline{\hspace{234pt}} Chair\\
    \hspace*{77pt}Dr.\@ W. Lucia\\[2.5ex]
     \hspace*{77pt}\underline{\hspace{234pt}} Supervisor \\
    \hspace*{77pt}Dr.\@ Jeremy Clark\\[2.5ex]
    \hspace*{77pt}\underline{\hspace{234pt}} CIISE Examiner\\
    \hspace*{77pt}Dr.\@ A. Youssef\\[2.5ex]
    \hspace*{77pt}\underline{\hspace{234pt}} External Examiner\\
    \hspace*{77pt}Dr.\@ F. McKelvey\\[2.5ex]
   
    Approved by \hspace{9pt}\underline{\hspace{232pt}}\\
    \hspace*{79pt}Dr.\@ C. Assi\\
    \hspace*{79pt}Graduate Program Director\\[6ex]
    \underline{\hspace*{110pt}} 2018. \hspace{64pt} \underline{\hspace{219pt}}\\
    \hspace*{213pt}Dr.\@ A. Asif\\
    \hspace*{213pt}Dean of ENCS